Dirac neutrino mass generation from Majorana messenger

### 2019-07-29 draft.tex
Updates from Overleaf

\section{The model}
\label{sec:Model}
As a preliminary model, we propose a model that includes an additional Higgs doublet with $ Y = -1/2 $. To forbid another terms, we used a $U(1)^{\prime}$ symmetry. This model is known as two Higgs doublets model (2HDM)~\cite{Davidson:2005cw}. Also, these symmetry allows us to forbid Dirac mass terms at tree level. Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $SU(2)_L$. The $U(1)^{\prime}$ charge for the new particles will be defined by the anomaly cancellation equations and the Yukawa interactions. In this model the neutrinos are Dirac fermions. Particle content and their respective charges are show in Tab.~\ref{tab:partcont}.

The most general Yukawa Lagrangian is:
%
\begin{align*}
\label{Eq:LagY}
    \mathcal{L} \subset& -[ 
    h^{a}_{i} \overline{L_{i}} \eta \psi_{a} +  y^{a}_{j} \overline{\nu_{R_{j}}} \sigma^{\dagger} \psi_{a} + y_{\psi}^{a b} \overline{\psi^{c}_{a}} \psi_{b} S + \text{h.c}] \\
    &- \mathcal{V}(H, H_{2}, S, \eta, \sigma)\,,
\end{align*}
%
where $L_{i}$ are the SM lepton doublets, $\eta = \left( \eta^{+} \ \eta^{0} \right)^{T}$, $\widetilde{\eta} = i \sigma_2 \eta^{\dagger}$ and $\mathcal{V}(H, H_{2}, S, \eta, \sigma)$ is the scalar potential. $h^{a}_i$ and $y^{a}_{j}$ ($i,j,a=1,2,3$) are matrix in flavor space.
%
\begin{table}
  \centering
  \begin{tabular}{|l|l|l|}
    \hline  
    Particles     & $\left( SU(2)_L, U(1)_Y \right)$ & $U(1)^{\prime}$ \\ \hline
    $H $  & $(2, 1/2)$ &  0 \\
    $\eta$ & $(2,1/2)$ & $1$ \\
    $S$ & $(1,0)$ & $2$ \\
    $\sigma$ & $(1,0)$ & $3$ \\
    \hline
    $Q_{L_{i}}$  & $(2,-1/6)$ & $0$ \\
    $\overline{u_{R_{i}}}$ & $(1,-2/3)$ & $0$ \\
    $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $0$ \\
    \hline
    $L_i$  & $(2,-1/2)$ & $0$ \\
    $\overline{e_{R_i}}$ & $(1,1)$ & $0$ \\
    $\overline{\nu_{R_{i,j}}}$ & $(1,0)$ & $4$\\
    $\overline{\nu_{R_k}}$ & $(1,0)$ & $-5$\\
    $\psi_{i}$  & $(1,0)$ & $-1$ \\\hline
  \end{tabular}
  \caption{Scalars and left-handed fermions with their respective charges.}
  \label{tab:partcont}
\end{table}
%

The most general gauge invariant scalar potential for this model is
%
\begin{align*}
    \mathcal{V}(H, S, \eta, \sigma) = & \mathcal{V}(H) + \mathcal{V}(S) + \mathcal{V}(\eta) + \mathcal{V}(\sigma) \\
    &+  \lambda_{3} (H^{\dagger} H ) (S^{\dagger} S) + \lambda_{4} (H^{\dagger} H ) (\sigma^{\dagger} \sigma ) + \lambda_{5} (H^{\dagger} H ) (\eta^{\dagger} \eta )\\
    &+ \lambda_{9} (S^{\dagger} S) (\sigma^{\dagger} \sigma ) + \lambda_{10} (S^{\dagger} S) (\eta^{\dagger} \eta ) + \lambda_{11} (\eta^{\dagger} \eta ) (\sigma^{\dagger} \sigma ) + \lambda_{12} (\eta^{\dagger} H ) (H^{\dagger} \eta ) \\
    &+ (\mu \eta^{\dagger} H S^{\dagger} \sigma + \text{h.c.})\,,
\end{align*}
%
where $\mathcal{V}(\omega) = \mu^{2}_{\omega} \omega^{\dagger} \omega + \lambda_{\omega} (\omega^{\dagger} \omega)^{2}/2$. We consider that the parameters are real, since we are not going to deal with the CP violation~\cite{Abe:2016sqa}.

>>>>

\section{The model}
\label{sec:Model}
As a preliminary model, we propose a model that includes an additional gauge symmetry $U(1)^{\prime}$.  Where  gauge invariance is used to forbid Dirac and Majorana mass terms at tree level. Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $SU(2)_L$. The $U(1)^{\prime}$ charge for the new particles will be defined by the anomaly cancellation equations and the gauge invariance in Yukawa interactions. In this model the neutrinos are Dirac fermions. Particle content and their respective charges are show in Tab.~\ref{tab:partcont}.

The most general Yukawa Lagrangian is:
%
\begin{align*}
\label{Eq:LagY}
    \mathcal{L} \subset& -[ 
    h^{a}_{i} \overline{L_{i}} \eta \psi_{a} +  y^{a}_{j} \overline{\nu_{R_{j}}} \sigma^{\dagger} \psi_{a} + y_{\psi}^{a b} \overline{\psi^{c}_{a}} \psi_{b} S + \text{h.c}] \\
    &- \mathcal{V}(H, S, \eta, \sigma)\,,
\end{align*}
%
where $L_{i}$ are the SM lepton doublets, $\eta = \left( \eta^{+} \ \eta^{0} \right)^{T}$, $\widetilde{\eta} = i \sigma_2 \eta^{\dagger}$ and $\mathcal{V}(H, S, \eta, \sigma)$ is the scalar potential. $h^{a}_i$ and $y^{a}_{j}$ ($i,j,a=1,2,3$) are matrix in flavor space.
%
\begin{table}
  \centering
  \begin{tabular}{|l|l|l|}
    \hline  
    Particles     & $\left( SU(2)_L, U(1)_Y \right)$ & $U(1)^{\prime}$ \\ \hline
    $H $  & $(2, 1/2)$ &  0 \\
    $\eta$ & $(2,1/2)$ & $1$ \\
    $S$ & $(1,0)$ & $2$ \\
    $\sigma$ & $(1,0)$ & $3$ \\
    \hline
    $Q_{L_{i}}$  & $(2,-1/6)$ & $0$ \\
    $\overline{u_{R_{i}}}$ & $(1,-2/3)$ & $0$ \\
    $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $0$ \\
    \hline
    $L_i$  & $(2,-1/2)$ & $0$ \\
    $\overline{e_{R_i}}$ & $(1,1)$ & $0$ \\
    $\overline{\nu_{R_{i,j}}}$ & $(1,0)$ & $4$\\
    $\overline{\nu_{R_k}}$ & $(1,0)$ & $-5$\\
    $\psi_{i}$  & $(1,0)$ & $-1$ \\\hline
  \end{tabular}
  \caption{Scalars and left-handed fermions with their respective charges.}
  \label{tab:partcont}
\end{table}
%

The most general gauge invariant scalar potential for this model is
%
\begin{align*}
    \mathcal{V}(H, S, \eta, \sigma) = & \mathcal{V}(H) + \mathcal{V}(S) + \mathcal{V}(\eta) + \mathcal{V}(\sigma) \\
    &+  \lambda_{1} (H^{\dagger} H ) (S^{\dagger} S) + \lambda_{2} (H^{\dagger} H ) (\sigma^{\dagger} \sigma ) + \lambda_{3} (H^{\dagger} H ) (\eta^{\dagger} \eta )\\
    &+ \lambda_{4} (S^{\dagger} S) (\sigma^{\dagger} \sigma ) + \lambda_{5} (S^{\dagger} S) (\eta^{\dagger} \eta ) + \lambda_{6} (\eta^{\dagger} \eta ) (\sigma^{\dagger} \sigma ) + \lambda_{7} (\eta^{\dagger} H ) (H^{\dagger} \eta ) \\
    &+ \mu (\eta^{\dagger} H S^{\dagger} \sigma + \text{h.c.})\,,
\end{align*}
%
where $\mathcal{V}(\omega) = \mu^{2}_{\omega} \omega^{\dagger} \omega + \lambda_{\omega} (\omega^{\dagger} \omega)^{2}/2$. We consider that the parameters are real, since we are not going to deal with the CP violation~\cite{Abe:2016sqa}.
